---
title: "Interactive Mapping with Leaflet"
author: "Altamash Ali"
date: "January 21, 2026"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(leaflet)
```

## Global Landmark Exploration
This document features an interactive map created using the leaflet package in R. The map below highlights the Eiffel Tower in Paris, France.

Click on the marker to see more information!

```{r}
# Define coordinates for the Eiffel Tower
lat <- 48.8584
lng <- 2.2945

# Create the interactive map
my_map <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=lat, lng=lng, 
             popup="<strong>Eiffel Tower</strong><br>Paris, France<br>Built in 1889")

my_map
```

## Summary
The map was generated using the following steps:

1. Initializing the leaflet object with `leaflet()`.
2. Adding geographic tiles with `addTiles()`.
3. Placing a marker with a customized HTML popup via `addMarkers()`

### Source Code
The full source code for this project is available on GitHub: 
[View Source on GitHub](https://github.com/realAltamashAli/Leaflet_Project)
